TR Invariant T.I.

### 2017-05-01 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] Improves cal of EdgeStates and ChernNumber.

    Numerical calculations can be performed in this case to find eigevectors
    whose eigevectors are close to zero. The result gives real edge states. For
    example, when $N=30$, below are a plot of eigevectors, whose eigenvalues
    $\epsilon$ satisfy $\abs{\epsilon}<0.2$:
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=30.EdgeState}.pdf}
        \caption{Edge states when $N=30$ (amplitudes have not been normalized).}
        \label{fig:InfiniteStrip/InfiniteStrip=30.EdgeState.pdf}
    \end{figure}

    \subsection{Berry Phase}
    \label{sec:Berry Phase}
    The easiest case when we can calculate the Berry phase is when we have
    translational invariance in both $x$ and $y$ direction. The
    Fourier-transformed Hamiltonian is then diagonal. 
    \begin{align}
        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
        \nonumber\\
        &\left[ \sin(p_x)\sigma^x + \sin(p_y)\sigma^y
            +(2-m-\cos(p_x)-\cos(p_y))\sigma^z
        \right] c_{p_x,p_y}
    \end{align}
    The Berry phase for a Hamiltonian of the form
    $\vec{d}(\vec{k})\vdot\vec{\sigma}$, is equal to $\pm\frac{1}{2}\Omega$,
    where the sign is determined by the choice of eigenstate, the $\Omega$ is
    the solid angle traversed by $\vec{d}$ as its parameter $\vec{k}$ varies,
    Now $\vec{d}=(\sin(p_x),\sin(p_y),2-m-\cos(p_x)-\cos(p_y))$, which is
    numerical explored\footnote{Details can be found in in file \menu{Attempts
    at Getting Chern Number.nb}.}.

>>>>

    Numerical calculations can be performed in this case to find eigevectors
    whose corresponding eigenvalues are close to zero. The result gives very
    good showcase of edge states. For example, when $N=30$, we plot its
    eigevectors (more precisely, the absolute value of each components of its
    eigenvectors) in Figure~\ref{fig:InfiniteStrip=30.EdgeState}.
    \footnote{Due to numerical problem, it is troublesome to plot eigenvectors
        corresponding to one band. But we could plot eigenvectors whose
        eigenvalues $\epsilon$ satisfy $\abs{\epsilon}<0.5$. This ensures that
        we select the eigenvectors from the crossing band. Also, for numerical
        accuracy in Mathematica's function \texttt{Eigensystem}, I used the "FEAST"
        method, since the ordinary method gave a state not localized at the boundary but
        at some point close to the boundary.}
    Also, it can be found in that there are one left-localized state and one right-localized state
    (figure~\ref{fig:InfiniteStrip=30.EdgeState.LeftRight}).

    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=30.EdgeState}.pdf}
        \caption{Edge states when $N=30$ (amplitudes have not been normalized).}
        \label{fig:InfiniteStrip=30.EdgeState}
    \end{figure}
\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=30.EdgeState.LeftRight}.pdf}
    \caption{The left-localized and right-localized states. The $(p_x,E_x)$ for
    two states $1,2$ are $(-0.05,0.0499792)$ and $(0.1,0.0998334)$
    respectively.}
    \label{fig:InfiniteStrip=30.EdgeState.LeftRight}
\end{figure}
    \subsection{Berry Phase}
    \label{sec:Berry Phase}
    The easiest case when we can calculate the Berry phase is when we have
    translational invariance in both $x$ and $y$ direction. The
    Fourier-transformed Hamiltonian is then diagonal. 
    \begin{align}
        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
        \nonumber\\
        &\left[ \sin(p_x)\sigma^x + \sin(p_y)\sigma^y
            +(2-m-\cos(p_x)-\cos(p_y))\sigma^z
        \right] c_{p_x,p_y}
    \end{align}
    The Berry phase for a Hamiltonian of the form
    $\vec{d}(\vec{k})\vdot\vec{\sigma}$, is equal to $\pm\frac{1}{2}\Omega$,
    where the sign is determined by the choice of eigenstate, the $\Omega$ is
    the solid angle traversed by $\vec{d}$ as its parameter $\vec{k}$ varies,
    Now $\vec{d}=(\sin(p_x),\sin(p_y),2-m-\cos(p_x)-\cos(p_y))$, which is
    numerical explored\footnote{Details can be found in in file \menu{Attempts
    at Getting Chern Number.nb}.}.
